STJ2012 analysis

### 2016-07-29 analysis/STJ2012_analysis.Rmd
add PERMANOVA analyses

>>>>

## Differences between species and shores
Whether *Symbiodinium* communities differ among species, or differ between north vs. south shores within species, is evaluated here using permutational analysis of variance (PERMANOVA).

```{r permanovas, cache=T}
# PERMANOVA for differences among species? Post-hoc: which spp are different?

# Compute within- and between-pool statistics for each Species
shorestats <- data.frame(matrix(dimnames=list(levels(data.frame(sample_data(phy.f.t))$Species), 
                                              c("Species", "n", "overall", "within", 
                                                "between", "R2", "bd", "p")), ncol=8, nrow=10))
for (i in 1:nlevels(data.frame(sample_data(phy.f.t))$Species)) {
  sp <- levels(data.frame(sample_data(phy.f.t))$Species)[i]
  shorestats$Species[i] <- sp
  phy.f.t.species <- subset_samples(phy.f.t, Species==sp)  # Set temp phyloseq object
  shorestats$n[i] <- nsamples(phy.f.t.species)
  md <- meandist(phyloseq::distance(phy.f.t.species, "bray"), 
                 sample_data(phy.f.t.species)$Shore)
  shorestats$within[i] <- summary(md)$W  # Weighted mean dissimilarity within both Pools
  shorestats$between[i] <- summary(md)$B  # Mean dissimilarity between Pools
  shorestats$overall[i] <- summary(md)$D  # Overall dissimilarity
  if (nlevels(as(sample_data(phy.f.t.species), "data.frame")$Shore) > 1) {
    set.seed(70235)
    permanova <- adonis(phyloseq::distance(phy.f.t.species, "bray") ~ Shore, 
                        data=as(sample_data(phy.f.t.species), "data.frame"), permutations=9999)
    shorestats$R2[i] <- permanova$aov.tab$"R2"[1]  # PERMANOVA partial R-squared
    shorestats$p[i] <- permanova$aov.tab$"Pr(>F)"[1]  # PERMANOVA p-value
    bd <- betadisper(phyloseq::distance(phy.f.t.species, "bray"),
                     group=as(sample_data(phy.f.t.species), "data.frame")$Shore)
    shorestats$bd[i] <- TukeyHSD(bd)$group[4]
  } else {
    shorestats$R2[i] <- NA
    shorestats$p[i] <- NA
    shorestats$bd[i] <- NA
  }
}
knitr::kable(shorestats)  # dendrogyra, porites furcata, and siderastrea siderea differ by shore
```
